MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-19 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
increment to dream 1.17.3

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(R.utils)
library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)

library(synapser)
library(knitr)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')

@@

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = tmp, 
                                                               formula = formula,
                                                               data = COVARIATES )

# Fit linear model using new weights and new design
# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES)

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(R.utils)
library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)
devtools::install_github("GabrielHoffman/variancePartition@3287d7b")
library(variancePartition)
library(synapser)
library(knitr)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')

@@

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = geneExpr, 
                                                               formula = formula,
                                                               data = COVARIATES)

# Fit linear model using new weights and new design
# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)
